Factors determining how catchments respond to forest cover change. Re-analysing global data sets.

### 2022-03-30 paper/Forest_and_Water/Forest_and_Water.Rmd
update link to github repos

All the final data and analysis for this paper are located on github: [https://github.com/WillemVervoort/Forest_and_water](https://github.com/WillemVervoort/Forest_and_water) on the "publish" branch.

>>>>

All the final data and analysis for this paper are located on github: [https://github.com/WillemVervoort/Forest_and_water](https://github.com/WillemVervoort/Forest_and_water/tree/publish) on the "publish" branch.

### 2022-03-30 paper/Forest_and_Water/Forest_and_Water.tex
update link to github repos

All the final data and analysis for this paper are located on github: \url{https://github.com/WillemVervoort/Forest_and_water} on the ``publish'' branch.

>>>>

All the final data and analysis for this paper are located on github: \href{https://github.com/WillemVervoort/Forest_and_water/tree/publish}{https://github.com/WillemVervoort/Forest\_and\_water} on the ``publish'' branch.
